Technical Report

### 2018-04-11 fully-abstract-comp/technical-report.tex
Comment out obsolete example, remove old back-translation section.

\clearpage
\section{Examples}
\subsection{Capability Opacity}
\label{subsec:capability-opacity}

\dominique{27-09-2017: Is this example still relevant? Isn't it solved differently by the variable-length-instructions idea?}
\lau{28-09-2017: It seems to me that this is indeed solved by the variable length instructions. That said, I would like to keep it around (maybe change it so it becomes an argument for variable length instructions).}
This example was introduced when we envisioned a capability machine with $\spush{}$, $\spop{}$, $\ssload{}{}$, $\scall{\offpc,\offsigma}{}{}$ and $\sreturn$ instructions. The below example is a motivation for having variable length instructions in the source language because if we have enough memory to ``do the same'' in the target language as in the source language, then the below example does not work.

The following pseudo program demonstrates the need of opaque capabilities. If we assume a system with no opaque capabilities, then the following programs break compiler correctness
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
p1 ::= if r1 is length 2 then
         call r1 with the following callback in r5:
           {put $\textit{\texttt{diverging}}$ closure in r2;
            return};
         halt
       else diverge

p2 ::= if r1 is length 2 then
         call r1 with the following callback in r5:
           {put $\textit{\texttt{terminating}}$ closure in r2;
            return};
         halt
       else diverge
\end{lstlisting}
The diverging closure could just contain $\sjmp{\pcreg}$, which diverges. The terminating closure could just be $\sreturn$.

The context with $r1$ as an executable capability pointing to:
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
$\scall{\offpc,\offsigma}{r5}{0}$
$\sjmp{r5}$
\end{lstlisting}
\footnote{At this time $\scall{\offpc,\offsigma}{}{}$ did argument spilling and it only takes one argument because we were considering enter capabilities.}distinguishes the two contexts, but two instructions are not enough to do the same at the target level. We would not have enough instructions to set up a proper return pointer for the compiled return to use.

\clearpage
\section{Back translation}
The back translation is an embedding of the target language into the source language.

>>>>

% \clearpage
% \section{Examples}
% \subsection{Capability Opacity}
% \label{subsec:capability-opacity}

% \dominique{27-09-2017: Is this example still relevant? Isn't it solved differently by the variable-length-instructions idea?}
% \lau{28-09-2017: It seems to me that this is indeed solved by the variable length instructions. That said, I would like to keep it around (maybe change it so it becomes an argument for variable length instructions).}
% This example was introduced when we envisioned a capability machine with $\spush{}$, $\spop{}$, $\ssload{}{}$, $\scall{\offpc,\offsigma}{}{}$ and $\sreturn$ instructions. The below example is a motivation for having variable length instructions in the source language because if we have enough memory to ``do the same'' in the target language as in the source language, then the below example does not work.

% The following pseudo program demonstrates the need of opaque capabilities. If we assume a system with no opaque capabilities, then the following programs break compiler correctness
% \begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
% p1 ::= if r1 is length 2 then
%          call r1 with the following callback in r5:
%            {put $\textit{\texttt{diverging}}$ closure in r2;
%             return};
%          halt
%        else diverge

% p2 ::= if r1 is length 2 then
%          call r1 with the following callback in r5:
%            {put $\textit{\texttt{terminating}}$ closure in r2;
%             return};
%          halt
%        else diverge
% \end{lstlisting}
% The diverging closure could just contain $\sjmp{\pcreg}$, which diverges. The terminating closure could just be $\sreturn$.

% The context with $r1$ as an executable capability pointing to:
% \begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
% $\scall{\offpc,\offsigma}{r5}{0}$
% $\sjmp{r5}$
% \end{lstlisting}
% \footnote{At this time $\scall{\offpc,\offsigma}{}{}$ did argument spilling and it only takes one argument because we were considering enter capabilities.}distinguishes the two contexts, but two instructions are not enough to do the same at the target level. We would not have enough instructions to set up a proper return pointer for the compiled return to use.
